Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-15 paper/paper.tex

We  need the  following proposition that  connects  liveness analysis  with
minefield semantics transitions. 
\begin{proposition}
\label{prop:correctness}
\begin{enumerate} 
\item   Consider  a   \LET\  definition:   \linebreak  $\pi\!\!\!:   (\LET~x
  \leftarrow~\ldots~\IN~e$, such  that there is  a use of $x$  in $e$,
  i.e.  an occurrence of $\LET~y~\leftarrow~s~in \ldots$, where $s$ is
  $(\CAR\ x)$, $(\CDR\ x)$  or $(+\ x\ y)$, or $(\SIF\  x\ e1\ e2)$ or
  $(\SRETURN\ x)$. Then the demand on $x$ at $\pi$ is non-null.
\item    Assume    that    a   \LET\    definition    $\pi:    (\LET~z
  \leftarrow~(\CONS~x~y)~\IN~e$  has an  occurrence  of $(\CAR~z)$  in
  $e$.  Then  the  liveness  of  $x$  at  $\pi$  includes  $\epsilon$.
  Similarly  if $e$  contains $(CDR~z)$,  then the  liveness of$y$  at
  $\pi$ includes $\epsilon$.
\end{enumerate}
\end{proposition}

@@

\begin{proof}
For a program  executing according to {\em minefield  semantics}, if a
\bang\ has to  occur then some variable which is  dereferenced must be
set to  $\bot$, between its  creation and  use points.  This  can only
happen if  the liveness of  the variable being dereferenced  was null.
From the lemma~\ref{lemma:no-calls-correctness} it  is clear that this
cannot happen. {\color{Myblue}  Too bad - self  reference!! Should this
  be Proposition~\ref{prop:correctness}? }
\end{proof}

>>>>

We  need the  following proposition that  connects  liveness analysis  with
minefield semantics transitions. 
\begin{proposition}
\label{prop:correctness}
\begin{enumerate} 
\item   Consider  a   \LET\  definition:   \linebreak  $\pi\!\!\!:   (\LET~x
  \leftarrow~\ldots~\IN~e$, such  that there is  a use of $x$  in $e$,
  i.e.  an occurrence of $\LET~y~\leftarrow~s~in \ldots$, where $s$ is
  $(\CAR\ x)$, $(\CDR\ x)$  or $(+\ x\ y)$, or $(\SIF\  x\ e1\ e2)$ or
  $(\SRETURN\ x)$. Then the demand on $x$ at $\pi$ is non-null.
\item    Assume    that    a   \LET\    definition    $\pi:    (\LET~z
  \leftarrow~(\CONS~x~y)~\IN~e$  has an  occurrence  of $(\CAR~z)$  in
  $e$.  Then  the  liveness  of  $x$  at  $\pi$  includes  $\epsilon$.
  Similarly  if $e$  contains $(\CDR~z)$,  then the  liveness of$y$  at
  $\pi$ includes $\epsilon$.
\end{enumerate}
\end{proposition}

@@

\begin{proof}
For a program  executing according to {\em minefield  semantics}, if a
\bang\ has to  occur then some variable which is  dereferenced must be
set to  $\bot$, between its  creation and  use points.  This  can only
happen if  the liveness of  the variable being dereferenced  was null.
From  the Proposition~\ref{prop:correctness}  it  is clear  that this  cannot
happen.
\end{proof}
